---
title: "Spectral backtests of unconditional coverage"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demonstrating tests of unconditional coverages in the spectralBacktest Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE, message=FALSE}
library(spectralBacktest)
library(purrr)
library(dplyr)
library(knitr)
set.seed(543)

```

The basic spectral Z-test is called with the routine `monospectral_Ztest()`.  

We two samples of PIT values.  The first (PIT1) has uniform distribution, which coincides with the null hypothesis.  The second (PIT2) has beta distribution with excess mass in the upper and lower tails. 

```{r fig.width=6, fig.height=4}

n <- 750
alfbet <- 0.8

PIT1 <- runif(n)
PIT2 <- rbeta(n,alfbet,alfbet)

hist(PIT2)

```

The spectral test is specified using a kernel list of type "mono" or "bi" or "multi". We want to run a set of tests, so specify a list of kernel lists.

```{r warning=FALSE}

alpha1 <- 0.95
alpha_star <- 0.99
alpha2 <- 0.995

BIN <- list( name = 'Binomial score at 99%',
             type = 'mono',
             nu = nu_discrete,
             support = alpha_star,
             param = 1 )

ZU3 <- list( name = 'Discrete Uniform 3',
             type = 'mono',
             nu = nu_discrete,
             support = c(alpha1, alpha_star, alpha2),
             param = c(1, 1, 1) )

ZE <- list( name = 'Epanechnikov',
            type = 'mono',
            nu = nu_epanechnikov,
            support = c(alpha1, alpha2),
            param = NULL )

ZU <- list( name = 'Uniform',
            type = 'mono',
            nu = nu_uniform,
            support = c(alpha1, alpha2),
            param = NULL )

ZLp <- list( name = 'LinearUp',
            type = 'mono',
            nu = nu_linear,
            support = c(alpha1, alpha2),
            param = 1 )
ZLn <- list( name = 'LinearDown',
            type = 'mono',
            nu = nu_linear,
            support = c(alpha1, alpha2),
            param = -1 )


ZLL <- list( name = 'linear/Linear',
             type = 'bi',
             nu = list(nu_linear, nu_linear),
             correlation = rho_linear_linear,
             support = c(alpha1, alpha2),
             param = list(-1,1) )

ZAE <- list( name = 'Arcsin/Epanechnikov',
             type = 'bi',
             nu = list(nu_arcsin, nu_epanechnikov),
             correlation = rho_arcsin_epanechnikov,
             support = c(alpha1, alpha2),
             param = list(NULL, NULL) )

ZQQ <- list( name = 'quadratic/Quadratic',
             type = 'bi',
             nu = list(nu_beta, nu_beta),
             correlation = rho_beta_beta,
             support = c(alpha1, alpha2),
             param = list(c(3,1), c(1,3)) )

ZQUQ <- list( name = 'quadratic/Uniform/Quadratic',
             type = 'multi',
             nu = list(nu_beta, nu_beta),
             correlation = rho_beta_beta,
             support = c(alpha1, alpha2),
             param = list(c(3,1), c(1,1), c(1,3)) )

PNS <- list( name = 'Probitnormal score',
             type = 'bi',
             nu = list(nu_probitnormal, nu_probitnormal),
             correlation = rho_probitnormal,
             support = c(alpha1, alpha2),
             param = list(1, 2) )

Pearson3 <- list(name = 'Pearson',
                 type = 'multi',
                 nu = nu_pearson,
                 correlation = rho_pearson,
                 support=NULL,
                 param=list(alpha1, alpha_star, alpha2))

# gather the tests into a list and execute!
kernlist <- list(BIN=BIN, Pearson3=Pearson3, ZU3=ZU3,
                 ZU=ZU, ZE=ZE, ZLp=ZLp, ZLn=ZLn,
                 ZLL=ZLL, ZAE=ZAE, PNS=PNS)

pval <- map_df(list(PIT1, PIT2), 
               function(P) lapply(kernlist, function(kern) spectral_Ztest(kern,P))) %>%
        mutate(PIT=c('Uniform',sprintf('Beta(%0.2f,%0.2f)',alfbet,alfbet))) %>%
        select('PIT', everything())

kable(pval, digits=4)

```

Now let's see how to assess the size and power of the test. We generate a large number of backtesting samples, and apply the same set of tests to each.  Results are gathered in a tibble.  We summarize the tibble by reporting the percentage of rejections (at the 5% level) for each test.  

To assess *size*, we need a uniform DGP, so set $a=b=1$. Ideally, the test will reject about 5% of the time. 

```{r warning=FALSE}

n <- 500
a <- b <- 1  # if a==b==1, we are assessing size of test
Npf <- 5000  # number of portfolios
rpval <- function(kernellist) {
  P <- rbeta(n,a,b)
  map(kernellist, ~spectral_Ztest(.x,P))
}

df <- rerun(Npf, rpval(kernlist)) %>%  map_df(`[`,names(kernlist))
rejectrate <- summarize_all(df, list(function(x) mean(x<=0.05)))
kable(rejectrate, digits=4, caption='Size. Frequency of test rejections at 5% level')

```

Finally, we assess the *power* of the tests against a non-uniform DGP. Here we want the test to reject as often as possible.

```{r warning=FALSE}

a <- b <- alfbet  
df <- rerun(Npf, rpval(kernlist)) %>%  map_df(`[`,names(kernlist))
rejectrate <- summarize_all(df, list(function(x) mean(x<=0.05)))
kable(rejectrate, digits=4, caption='Power. Frequency of test rejections at 5% level')

```
